Paper_stuff

### 2023-09-14 Paper_stuff.Rmd
Duration categories aren't working as they are suppsoed to.

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,2000))+
  coord_flip()+
  facet_wrap(~Duration)
```

@@

### plot means based upon duration group membership 
•	Visualization – RDQ pre and post change.
•	Table or Visualization – Reasons for discharge results.

>>>>

# ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
#   geom_bar()+
#   ggtitle("Frequency of Psychiatric Disorder Subtypes") +
#   theme(axis.text.x = element_text(angle = 45,hjust = 1),
#         legend.position = "none")+
#   xlab("Psychiatric Disorder Subtype")+
#   theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
#   theme(panel.background=NULL)+
#   scale_y_continuous(name = "Frequency",limits=c(0,2000))+
#   coord_flip()+
#   facet_wrap(~Duration)
```

@@

### plot means based upon duration group membership

•	Visualization – RDQ pre and post change.
•	Table or Visualization – Reasons for discharge results.
